\newpage
{\Huge \bf Abstract}
\vspace{24pt} 

This project seeks to apply deep reinforcement learning (RL) techniques with graph neural networks to the space of intradomain traffic engineering in order to minimise link congestion. Recently, there has been work in this space from Valadarsky et al. in the paper ``Learning to route with Deep RL'' where the authors achieved some success using RL with a multilayer perceptron (MLP) policy architecture. However, this approach suffers from a level of rigidity in that it cannot easily generalise to new networks or traffic types.

Aside from this work, there has been an explosion of research into graph neural networks (GNNs) which are a class of neural network the operates specifically on the structure of graphs. These make it easier to create only the intended relational inductive biases in policy design and have had much success in many fields, especially in terms of generalising solutions across different graphs.

In this project, we aim to combine these two ideas: the routing methods from Valadarsky et al. with GNNs to allow for generalisation. We provide a new environment in which different strategies can be implemented and tested, including different types of policy, traffic, and utility function. We also present the design of GNN-based policies that seek to solve this problem. Finally, we provide a comprehensive assessment of the different techniques, with a particular focus on their capability to generalise to different traffic patterns and network topologies.

\newpage
\vspace*{\fill}
